---
title: "Combining Census data with the Same Sex Marriage Survey in R"
author: "Miles McBain"
date: "November 25, 2017"
output: html_document
---

# Load SSM data

```{r}
library(readr)
ssm_response <- read_csv("./SSM_AUS_Response.csv") %>%  
  mutate(State = gsub("TAS", "Tas.", State))
ssm_participation <- read_csv("./SSM_AUS_Participation.csv")

```

# Get Census Data
We ignore all the reports and go straight for the 'datapacks' at https://datapacks.censusdata.abs.gov.au/datapacks/. These are geographically summarised views of the data. To get a datapack we have to make two choices regarding the how the summaries are made:
1. 'Type' which cocerns questions like: do you want to summarise by people's place of residence or by place where they filled out the census form? For a postal survey we want the the data summarised by place of residence which is the 'General Community Profile' datapack. 

1. Geographical area used for summarise. To match the postal survey data we choose 'Commonwealth Electoral Divisions'.

If you'd prefer not to do this you can use my [`fetch_data.R` script]() to fetch and decompress the datapack to `./data`

# Navigating the Data Pack
The datapack consists of 59 encoded csv files and 3 metadata excel files that will help us decode their meaning. What? You didn't think this was going to be straight forward did you? When I say encoded, I mean the csv's have inscrutable names like `2016Census_G09C.csv` and contain column names like `Se_d_r_or_t_h_t_Tot_NofB_0_ib` (H.T. @hughparsonage).

```{r}
library(readxl)
electorate_codes <- read_excel(
  path = "./data/Metadata/2016Census_geog_desc_1st_and_2nd_release.xlsx",
  sheet = "2016_ASGS_Non-ABS_Structures")

column_codes <- read_excel(
  path = "./data/Metadata/Metadata_2016_GCP_DataPack.xlsx",
  sheet = "Cell descriptors information",
  skip = 10)
```

# Religious Affiliation
```{r}
library(tidyverse)

religious_affiliation_by_person <-
  read_csv(
    file = "data/2016 Census GCP Commonwealth Electoral Divisions for AUST/2016Census_G14_AUS_CED.csv")

names(religious_affiliation_by_person)[-1] <- 
  column_codes$Long[match(names(religious_affiliation_by_person), column_codes$Short)[-1]]

religion <-
  religious_affiliation_by_person %>%
  mutate(prop_christian_and_muslim = ((Christianity_Total_Persons + Islam_Persons)/Total_Persons)*100 ) %>%
  left_join(electorate_codes, by = c("CED_CODE_2016" = "Census_Code_2016"))
  
religion_vs_no <- 
  ssm_response %>%
  left_join(religion, by = c("area" = "Census_Name_2016")) %>%
  select(area, prop_christian_and_muslim, `No pct`, State)

```
## A plot
```{r}
library(ggplot2)
religion_vs_no %>%
  ggplot(aes(x = `No pct`, y = prop_christian_and_muslim, colour= State, label = area)) +
  geom_point() +
  facet_wrap(~State) +
  theme(legend.position = "none")
```


# Won't Somebody Think of the Children
```{r}
family_composition <- 
  read_csv("data/2016 Census GCP Commonwealth Electoral Divisions for AUST/2016Census_G25_AUS_CED.csv")

names(family_composition)[-1] <- 
  column_codes$Long[match(names(family_composition), column_codes$Short)[-1]]

families_with_young_children <- 
  family_composition %>%
  mutate(pct_young_children = (Couple_family_with_children_under_15_and_no_dependent_students_and_no_non_dependent_children_Persons/Total_Persons)*100) %>%
  left_join(electorate_codes, by = c("CED_CODE_2016" = "Census_Code_2016"))

families_with_young_children_vs_no <-
  ssm_response %>%
  left_join(families_with_young_children, by = c("area" = "Census_Name_2016")) %>%
  select(area, pct_young_children, `No pct`, State)

families_with_young_children_vs_no %>%
  ggplot(aes(x = pct_young_children, y = `No pct`)) +
  geom_point() + 
  facet_wrap(~State)

```


